### 2016-08-17 latex/paper.tex
Tc non-dimensional

Following the approach of Smith~\cite{Smith1901a} and Pippard~\cite{Pippard1932d}, we will approximate the spoke system as a continuum which exerts a distributed load on the rim. The stiffness per unit length is defined by the sum of the spoke stiffnesses in one periodic grouping of spokes, divided by the arc length of the grouping.
	\begin{equation}\label{eq:kbar}
	\bar{\bm{k}} = \frac{1}{2\pi R}\left(\frac{n_s}{n_p}\right) \sum_i^{n_p} \bm{k}_{f, i}
	\end{equation}
	The distributed load $\bar{\bm{f}}$ does an amount of work per unit length equal to
	\begin{equation}\label{eq:w_spokes}
	\bar{w} = \int_0^{u_n} \bar{\bm{f}} \cdot d\bm{u}_n = \frac{1}{2} \bm{u}_n \cdot \bar{\bm{k}} \cdot \bm{u}_n
	\end{equation}
The line of action is assumed to pass sufficiently close to the rim shear center that any difference between the displacement of the spoke nipple and the displacement of the shear center can be ignored. Therefore $\bm{u}_n = \bm{u}$. Substituting a lateral buckling displacement $\bm{u}=u\hat{\bm{e}}_1$ into Eqn. \ref{eq:w_spokes} and integrating over the length of the rim gives the strain energy stored in the spoke system.
	\begin{equation}\label{eq:Us}
	U_{spokes} = \int_0^{2\pi} \bar{w} \, ds = \frac{1}{2} \bar{k}_{uu}u^2
	\end{equation}

@@

The buckled shape of the wheel must be periodic, so we assume a buckled shape of the form
	\begin{equation}\label{eq:modeshape}
	\begin{split}
	u &= \delta u_n \cos{\frac{ns}{R}} \\
	\phi &= \delta\phi_n \cos{\frac{ns}{R}}
	\end{split}
	\end{equation}
The wheel becomes unstable when the increase in strain energy is exactly balanced by the virtual work for a perturbing displacement $\delta u_n, \delta\phi_n$, i.e. when the total potential energy is zero.
	\begin{equation}\label{eq:TotPot}
	\Pi = U_{rim} + U_{spokes} - V_{rim} = 0
	\end{equation}
Substituting the buckling mode shape Eqn. \ref{eq:modeshape} into Eqns. \ref{eq:Urim}, \ref{eq:Vrim}, and \ref{eq:Us} and substituting into Eqn. \ref{eq:TotPot} yields a buckling criterion for the $n$th mode.
	\begin{multline}\label{eq:BuckCrit}
	\frac{\pi EI_{11}}{R^3}(n^2 u_n - R\phi_n)^2 + \frac{\pi n^2}{R^2}\left(GJ + \frac{EI_w}{R^2}n^2\right)(u_n-R\phi_n)^2 + \\
	\pi R(\bar{k}_{uu}^{el} + T\bar{k}_{uu}^{el})u_n^2 - N_r\frac{\pi n^2}{R}u_n^2=0
	\end{multline}
Equation \ref{eq:BuckCrit} has a quadratic form and can be written using matrix notation:
	\begin{equation}\label{eq:Qform}
	\begin{bmatrix}
	u_n\\\phi_n
	\end{bmatrix} \cdot
	\begin{bmatrix}
	\frac{\partial^2 \Pi}{\partial u_n^2} & \frac{\partial^2 \Pi}{\partial u_n \partial \phi_n}\\
	\frac{\partial^2 \Pi}{\partial u_n\partial\phi_n} & \frac{\partial^2 \Pi}{\partial \phi_n^2}
	\end{bmatrix} \cdot
	\begin{bmatrix}
	u_n\\\phi_n
	\end{bmatrix}
	=0
	\end{equation}
Non-trivial solutions of Eqn. \ref{eq:Qform} exist when the determinant of the matrix vanishes. Substituting Eqn. \ref{eq:TN} for $N_r$ and solving Eqn. \ref{eq:BuckCrit} for $T$ gives the critical spoke tension for the $n$th mode.
	\begin{equation}
	...
	\end{equation}

\section{CONCLUSIONS}

>>>>

Following the approach of Smith~\cite{Smith1901a} and Pippard~\cite{Pippard1932d}, we will approximate the spoke system as a continuum which exerts a distributed load on the rim. The stiffness per unit length is defined by the sum of the spoke stiffnesses in one periodic grouping of spokes, divided by the arc length of the grouping.
	\begin{equation}\label{eq:kbar}
	\bar{\bm{k}} = \frac{1}{2\pi R}\left(\frac{n_s}{n_p}\right) \sum_i^{n_p} \bm{k}_{f, i}
	\end{equation}
	The distributed load $\bar{\bm{f}}$ does an amount of work per unit length equal to
	\begin{equation}\label{eq:w_spokes}
	\bar{w} = \int_0^{u_n} \bar{\bm{f}} \cdot d\bm{u}_n = \frac{1}{2} \bm{u}_n \cdot \bar{\bm{k}} \cdot \bm{u}_n
	\end{equation}
The line of action is assumed to pass sufficiently close to the rim shear center that any difference between the displacement of the spoke nipple and the displacement of the shear center can be ignored. Therefore $\bm{u}_n = \bm{u}$. Substituting a lateral buckling displacement $\bm{u}=u\hat{\bm{e}}_1$ into Eqn. \ref{eq:w_spokes} and integrating over the length of the rim gives the strain energy stored in the spoke system.
	\begin{equation}\label{eq:Us}
	U_{spokes} = \int_0^{2\pi} \bar{w} \, ds = \frac{1}{2} \bar{k}_{uu}u^2
	\end{equation}
The continuum stiffness can be written $\bar{\bm{k}} = \bar{\bm{k}}^{el} + T\bar{\bm{k}}^{tens}$, where the dependence on $T$ is shown explicitly. A very close approximation for the $\bar{k}_{uu}$ component for a symmetrically dished wheel is given by
	\begin{equation}\label{eq:kuu}
	\bar{k}_{uu} = \frac{n_sE_sA_s}{2\pi Rl}\sin^2{\alpha} + \frac{n_s T}{2\pi Rl}
	\end{equation}

@@

The buckled shape of the wheel must be periodic, so we assume a buckled shape of the form
	\begin{equation}\label{eq:modeshape}
	\begin{split}
	u &= \delta u_n \cos{\frac{ns}{R}} \\
	\phi &= \delta\phi_n \cos{\frac{ns}{R}}
	\end{split}
	\end{equation}
The wheel becomes unstable when the increase in strain energy is exactly balanced by the virtual work for a perturbing displacement $\delta u_n, \delta\phi_n$, i.e. when the total potential energy is zero.
	\begin{equation}\label{eq:TotPot}
	\Pi = U_{rim} + U_{spokes} - V_{rim} = 0
	\end{equation}
Substituting the buckling mode shape Eqn. \ref{eq:modeshape} into Eqns. \ref{eq:Urim}, \ref{eq:Vrim}, and \ref{eq:Us} and substituting into Eqn. \ref{eq:TotPot} yields a buckling criterion for the $n$th mode.
	\begin{multline}\label{eq:ECrit}
	\frac{\pi EI_{11}}{R^3}(n^2 u_n - R\phi_n)^2 + \frac{\pi n^2}{R^2}\left(GJ + \frac{EI_w}{R^2}n^2\right)(u_n-R\phi_n)^2 + \\
	\pi R(\bar{k}_{uu}^{el} + T\bar{k}_{uu}^{el})u_n^2 - N_r\frac{\pi n^2}{R}u_n^2=0
	\end{multline}
The torsional rigidity and warping rigidity can be combined into an effective torsional stiffness $\widetilde{GJ} = GJ + n^2EI_w/R^2$. Equation \ref{eq:ECrit} has a quadratic form and can be written using matrix notation:
	\begin{equation}\label{eq:Qform}
	\begin{bmatrix}
	u_n\\\phi_n
	\end{bmatrix} \cdot
	\begin{bmatrix}
	\frac{\partial^2 \Pi}{\partial u_n^2} & \frac{\partial^2 \Pi}{\partial u_n \partial \phi_n}\\
	\frac{\partial^2 \Pi}{\partial u_n\partial\phi_n} & \frac{\partial^2 \Pi}{\partial \phi_n^2}
	\end{bmatrix} \cdot
	\begin{bmatrix}
	u_n\\\phi_n
	\end{bmatrix}
	=0
	\end{equation}
Non-trivial solutions of Eqn. \ref{eq:Qform} exist when the determinant of the matrix vanishes. Expanding the determinant in Eqn. \ref{eq:Qform} and substituting Eqn. \ref{eq:TN} yields a linear equation for the critical buckling tension of the $n$th mode.
	\begin{multline}\label{eq:Tc_eq}
	\left(\frac{2\pi EI_{22}}{R}+\frac{2\pi \widetilde{GJ}n^2}{R} \right) \left( \frac{2\pi \widetilde{GJ}n^2}{R^3} + \frac{2\pi EI_{22}n^4}{R^3} + 2\pi R\bar{k}_{uu}^{el} + \frac{n_sT_{c,n}}{l} - \frac{n_sn^2T_{c,n}}{R}\right)\\
	- \left( \frac{2\pi EI_{22}n^2}{R^2} + \frac{2\pi \widetilde{GJ}n^2}{R^2} \right)^2 = 0
	\end{multline}
Solving Eqn. \ref{eq:Tc_eq} for $T_{c,n}$ yields the tension at which the $n$th mode becomes unstable. The critical buckling tension $T_c$ is the minimum $T_{c,n}$ with respect to the mode number $n\geq 2$.

\section{BUCKLING DUE TO INTERNAL FORCES}
The solution to Eqn. \ref{eq:Tc_eq} can be written in non-dimensional form as
	\begin{equation}\label{eq:Tc_nondim}
	\frac{T_{c,n}}{T_e} = \left( \frac{\tilde{u}n^2(n^2-1)^2}{1+\tilde{\mu}n^2} + \lambda \right) \left(\frac{1}{n^2-1} \right)
	\end{equation}
where the ``Euler tension'' $T_e=2\pi EI_{22}/n_sR^2$ is the tension that would produce a compressive force in the rim equal to the classical buckling load for a straight beam-column of length $2\pi R$. The parameter $\tilde{\mu} = \widetilde{GJ}/EI_{22}$ is the ratio of the effective torsional stiffness to the lateral bending stiffness. The parameter $\lambda = \bar{k}_{uu}^{el}R^4/EI_{22}$ is the ratio of the spoke system stiffness $\bar{k}_{uu}^{el}R$ to the rim bending stiffness $EI_{22}/R^3$.

\section{SUB-CRITICAL BUCKLING UNDER LATERAL LOADS}
...

\section{CONCLUSIONS}
...
